\documentclass{PoS}

\title{Searches with early data at CMS}

\ShortTitle{Searches with early data at CMS}

\author{\speaker{Francesco Santanastasio}%
        %\thanks{A footnote may follow.}\\
       University of Maryland, MD, USA\\
       E-mail: \email{francesco.santanastasio@cern.ch}}

%\author{Another Author\\
%        Affiliation\\
%        E-mail: \email{...}}

\abstract{This paper presents an overview of prospects for searches for new physics 
beyond the Standard Model with early data of the CMS experiment, at the Large Hadron Collider of CERN. 
The results presented here are based on Monte Carlo simulations of the 
CMS detector, assuming 10-100~pb$^{-1}$ of collected integrated 
luminosity and proton-proton collisions at $\sqrt{s} = 7$~TeV. 
A selection of benchmark analyses feasible with early data is discussed,  
including searches for new physics in the di-jet, lepton-jet, and di-lepton channels, 
the description of several techniques to identify the production of heavy long-lived charged particles, 
and search for evidence of Supersymmetry using di-lepton mass edges.}

\FullConference{XVIII International Workshop on Deep-Inelastic Scattering and Related Subjects\\
   April 19 -23, 2010\\
    Convitto della Calza, Firenze, Italy}

\begin{document}

\section{Introduction}
This paper presents a brief overview of prospects for searches for new physics, 
beyond the Standard Model (SM) of fundamental interactions, feasible with early data of the 
CMS experiment~\cite{Bayatian:2006zz}, at the Large Hadron Collider (LHC) of CERN.
At the time of the conference (April 2010), the LHC delivered a fraction of nb$^{-1}$ 
of pp collisions at $\sqrt{s} = 7$~TeV. While writing these proceedings 
(beginning of June 2010), the integrated luminosity recorded by the CMS experiment is 
around 20~nb$^{-1}$, and the expectation is to collect approximatly 150~nb$^{-1}$ of data
by the middle of July, in time for the ICHEP summer conference. 
The results presented at the conference, and here summarized, 
are therefore based on detailed Monte Carlo (MC) simulations of 
the CMS detector, assuming 10-100~pb$^{-1}$ 
of collected integrated luminosity and proton-proton collisions 
with a center-of-mass energy of $\sqrt{s} = 7$~TeV. 
A selection of several benchmark analyses with different experimental 
signatures is discussed. 

\begin{thebibliography}{0}
%%%%%%%%%%
%%%%%%%%%%
%@Article{Bayatian:2006zz,
%     author    = ``Bayatian, G. L. and others'',
% collaboration = ``CMS'',
%     title     = ``{CMS physics: Technical design report}'',
%     note     = ``CERN-LHCC-2006-001''
%}
%\cite{Bayatian:2006zz}
\bibitem{Bayatian:2006zz}
  G.~L.~Bayatian {\it et al.}  [CMS Collaboration],
  ``CMS physics: Technical design report''
  %%CITATION = CMS-TDR-008-1;%%
 \quad
 G.~L.~Bayatian {\it et al.}  [CMS Collaboration],
 ``CMS technical design report, volume II: Physics performance,''
 J.\ Phys.\ G {\bf 34} (2007) 995.
 %%CITATION = JPHGB,G34,995;%%

\end{thebibliography}

\end{document}
