
%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Francesco Santanastasio
\documentclass[10pt]{letter}
\setlength{\voffset}         {-2.0cm}
\setlength{\hoffset}         {-2.4cm}
\setlength{\textwidth}       {17.0cm}
\setlength{\textheight}      {24cm}


\pagestyle{empty}

% needed for customized page numbering
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
%\fancyfoot[R]{\footnotesize Page \thepage\ of \pageref{LastPage} }
\fancyfoot[R]{\footnotesize Francesco Santanastasio - Lista delle pubblicazioni allegate - Pag. \thepage\ di 2 }
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\begin{document}

{\large \sc \bf Francesco Santanastasio - Lista delle pubblicazioni allegate}



%--------------------------------------------------------------------------------
\begin{center} \textit{Pubblicazioni selezionate} \end{center}

\begin{enumerate}
\item A.~Bartoloni {\it et al.},
  ``High voltage system for the CMS electromagnetic calorimeter,''
  Nucl.\ Instrum.\ Meth.\  A {\bf 582} (2007) 462.
  %%CITATION = NUIMA,A582,462;%%
\item P.~Adzic {\it et al.}  [CMS Electromagnetic Calorimeter Group],
  ``Intercalibration of the barrel electromagnetic calorimeter of the CMS
  experiment at start-up,'' JINST {\bf 3} (2008) P10007.
  %%CITATION = JINST,3,P10007;%%
\item S.~Abdullin {\it et al.}  [USCMS Collaboration and ECAL/HCAL Collaboration],
  ``The Cms Barrel Calorimeter Response To Particle Beams From 2-Gev/C To 350-Gev/C,''
  Eur.\ Phys.\ J.\  C {\bf 60} (2009) 359.
  %%CITATION = EPHJA,C60,359;%%
\item S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  ``Identification and filtering of uncharacteristic noise in the CMS hadron calorimeter,''
  JINST {\bf 5} (2010) T03014
\item S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  ``Commissioning of the CMS Experiment and the Cosmic Run at Four Tesla,''
  JINST {\bf 5} (2010) T03001
\item S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  ``Performance of the CMS hadron calorimeter with cosmic ray muons and LHC beam data,''
  JINST {\bf 5} (2010) T03012
\item S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  ``Performance of CMS hadron calorimeter timing and synchronization using test beam, cosmic ray, and LHC beam data,''
  JINST {\bf 5} (2010) T03013

%--------------------------------------------------------------------------------
~\\
\begin{center} \textit{Pubblicazioni (Proceedings) per conferenze} \\ 
\end{center}

\item F. ~Santanastasio, ``Prospects for Exotica Searches at ATLAS and CMS Experiments'', 
  Il Nuovo Cimento Vol.32 C, N.3-4 ncc9484 (2009)

%--------------------------------------------------------------------------------
~\\
\begin{center} \textit{Altri documenti pubblici selezionati} \\ \end{center}

\item CMS Collaboration, 
  ``Search for Pair Production of First Generation Scalar Leptoquarks at the CMS Experiment,''
  CMS Physics Analysis Summaries, CMS-PAS-EXO-08-010 (2009) \\
  http://cdsweb.cern.ch/record/1196076/files/EXO-08-010-pas.pdf 

\item CMS Collaboration,
  ``Performance of Missing Transverse Energy Reconstruction in $\sqrt{s}=$ 900 and 2360 GeV pp Collision Data'',
  CMS Physics Analysis Summaries, CMS-PAS-JME-10-002 (2010) \\
  http://cdsweb.cern.ch/record/1247385/files/JME-10-002-pas.pdf

%--------------------------------------------------------------------------------
~\\
\begin{center} \textit{Altre pubblicazioni} \\ \end{center}

\item T.~C.~Collaboration  [CMS Collaboration],
  ``Transverse momentum and pseudorapidity distributions of charged hadrons in pp collisions at sqrt(s) = 0.9 and 2.36 TeV,''
  JHEP {\bf 1002} (2010) 041
\item S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  ``Performance of the CMS Level-1 trigger during commissioning with cosmic ray muons and LHC beams,''
  JINST {\bf 5} (2010) T03002
\item S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  ``Commissioning of the CMS High-Level Trigger with cosmic rays,''
  JINST {\bf 5} (2010) T03005
\item S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  ``Performance and operation of the CMS electromagnetic calorimeter,''
  JINST {\bf 5} (2010) T03010
\item S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  ``Measurement of the muon stopping power in lead tungstate,''
  JINST {\bf 5} (2010) P03007
\item S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  ``Commissioning and performance of the CMS pixel tracker with cosmic ray muons,''
  JINST {\bf 5} (2010) T03007
\item S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  ``Commissioning and performance of the CMS silicon strip tracker with cosmic ray muons,''
  JINST {\bf 5} (2010) T03008
\item S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  ``Performance of the CMS drift tube chambers with cosmic rays,''
  JINST {\bf 5} (2010) T03015
\item S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  ``Performance study of the CMS barrel resistive plate chambers with cosmic rays,''
  JINST {\bf 5} (2010) T03017
\item S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  ``Performance of the CMS cathode strip chambers with cosmic rays,''
  JINST {\bf 5} (2010) T03018


\end{enumerate}

\end{document}
